### 2024-08-19 paper.tex
start reorganizing linear algebra facts
start with irred components

\begin{lemma}
    Here we have an alternative characterization of \(B_{I, (\rho_i)}\).
    Namely,
    \[B_{I, (\rho_i)} = \{b \in \mathbb{C}^m : \forall i \in I. \; p_i = \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
    \[\textrm{ where } k = ...\}\]
\end{lemma}
\begin{proof}
    TODO
\end{proof}

\begin{corollary}

@@

\begin{lemma}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
The irreducible components of \(U_{I, (\rho_i)}\) are blah.
Thus, the irreducible components of \(U_0\) are blah.

@@

\section{Finding a centralizer}

@@

\section{A Jordan basis for \(A_{X, a, b}\)}

>>>>

\begin{lemma}\label{alternative_bs}
    Here we have an alternative characterization of \(B_{I, (\rho_i)}\).
    Namely,
    \[B_{I, (\rho_i)} = \{b \in \mathbb{C}^m : \forall i \in I. \; p_i = \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
    \[\textrm{ where } k = ...\}\]
\end{lemma}
\begin{proof}
    TODO
\end{proof}

\begin{corollary}\label{bs_iso}

@@

\begin{lemma}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
\begin{lemma}
    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties of the form
    \[\{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
    There are blah of these, and each has dimension blah.
\end{lemma}
\begin{proof}
    Components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously blah.
    Their dimensions are blah, and there are... of them.
    taking image under the isomorphism gives the desired result.
\end{proof}
From \cref{bs_iso}, we know that \(B_{I, (\rho_i)}\) is irreducible, of dimension blah.

The irreducible components of \(U_{I, (\rho_i)}\) are blah.
Thus, the irreducible components of \(U_0\) are blah.

@@

\section{Self-contained linear algebra facts}
\subsection{The centralizer of a nilpotent matrix}
\begin{definition}
    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
\end{definition}
\begin{definition}
    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, only the lower 
\end{definition}

@@
